Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
minor changes in examples

The object property \CodeIn{valueOf} stores a function
that returns a primitive value identifying the target
object~\cite{valueof}. The original version of this code returns an
empty string whereas the version of the code modified by the \radamsa{}
fuzzer~\cite{radamsa} returns a string representation of a null
character (\CodeIn{NUL} in ascii). The unary plus expression
``\CodeIn{+a}", used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary plus to
NaN as expected, as the null character cannot be converted. As result,
the test fails as expected. \chakra{}, in contrast, incorrectly
converts the string to zero, making the test to pass. All other
engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

\Mar{---------------------- estou aqui}

\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.  The code
snippet below shows the test input we used to reveal a bug in \veight.

%% eval(
%% "{ 
%%     function f() { 
%%       return 'declaration'; 
%%     } 
%%  }
%%  assert.sameValue(typeof f, 'function');
%%  \assert.sameValue(f(), 'declaration');"
%% );
%% // Fuzzed file

@@

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. Instead of the long integer passed as
argument to \CodeIn{"foo".repeat()}, the original test used the
integer literal 3. The engine crashes on this input as result. The
team answered that this was an incompatibility by design as the
function repeat was not expected to receive such a long value.

>>>>

The object property \CodeIn{valueOf} stores a function
that returns a primitive value identifying the target
object~\cite{valueof}. The original version of this code returns an
empty string whereas the version of the code modified by the \radamsa{}
fuzzer~\cite{radamsa} returns a string representation of a null
character (\CodeIn{NUL} in ascii). The unary plus expression
``\CodeIn{+a}", used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} \Igor{
  \chakra{} converte incorretamente o valor hexadecimal para
  0 e a expressao +0 resulta em 0, o que faz com que o teste passe. Os outros
  engines consideram o hexadecimal invalido (valor esperado), 
  quando o hexadecimal nao pode ser convertido, espera-se que retorne NaN, que +NaN resulta em NaN.
  }evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}
\Igor{
  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
  function declaration. The fuzzer removes the function declaration and 
  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
  the break statement should throw an early error (in this case a SyntaxError) 
  if the break statement is not nested in an iterational or a switch statement. All engines works
  as expected but \veight{} pass without failures.
}

@@

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.
